Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-15 prob.tex
prob.tex \section{Proofs} Add a definition~~

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}
\usepackage{tensor}
\newcommand{\rme}{\mathrm{e}}
\newcommand{\rmi}{\mathrm{i}}
\usepackage[braket]{qcircuit} 
\newcommand{\xyR}[1]{\xymatrixrowsep={#1}}
\newcommand{\xyC}[1]{\xymatrixcolsep={#1}}
\newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}
\newcommand{\melem}[3]{\ensuremath{\left\langle{#1}\middle\vert{#2}\middle\vert{#3}\right\rangle}}
\newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
\newcommand{\pr}[2]{\ip{#1}{#2}}
\newcommand{\proj}[1]{\op{#1}{#1}}

@@

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{blue}{Andy says: #1}\end{minipage}}}
\usepackage{tensor}
\newcommand{\rme}{\mathrm{e}}
\newcommand{\rmi}{\mathrm{i}}
\usepackage[braket]{qcircuit} 
\newcommand{\xyR}[1]{\xymatrixrowsep={#1}}
\newcommand{\xyC}[1]{\xymatrixcolsep={#1}}
\newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}
\newcommand{\melem}[3]{\ensuremath{\left\langle{#1}\middle\vert{#2}\middle\vert{#3}\right\rangle}}
\newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
\newcommand{\pr}[2]{\ip{#1}{#2}}
\newcommand{\proj}[1]{\op{#1}{#1}}
\usepackage{mnsymbol}
\newcommand{\HermitianForm}[2]{\ensuremath{\left\llangle{#1}\middle\vert{#2}\right\rrangle}}

@@

\begin{definition}\cite{gleason1957,RichmanBridges1999,Jaeger2007}~On
any complex vector space~$\mathbb{C}^{d}$, a (positive-definite)
Hermitian form~$\HermitianForm{.}{.}:\mathbb{C}^{d}\times\mathbb{C}^{d}\rightarrow\mathbb{C}$
is a function satisfying:
\item $\HermitianForm{\phi}{\alpha_{0}\psi_{0}+\alpha_{1}\psi_{1}}=\alpha_{0}\HermitianForm{\phi}{\psi_{0}}+\alpha_{1}\HermitianForm{\phi}{\psi_{1}}$,
where $\alpha_{0}$ and $\alpha_{1}\in\mathbb{C}$; $\ket{\phi}$,
$\ket{\psi_{0}}$, and $\ket{\psi_{1}}\in\mathbb{C}^{d}$\footnote{Notice that in the mathematical literature~\cite{RichmanBridges1999},
a Hermitian form is usually defined to be linear in the first complement,
and conjugate linear in the second complement.}.
\item $\HermitianForm{\phi}{\psi}=\HermitianForm{\psi}{\phi}^{*}$ for all
$\ket{\phi}$ and $\ket{\psi}\in\mathbb{C}^{d}$.
\item $\HermitianForm{\phi}{\phi}>0$ for all $\ket{\phi}\in\mathbb{C}^{d}\backslash\left\{ 0\right\} $.
\qed\end{definition}
